Desain dan Implementasi Pengumpulan Data Menggunakan \textit{Mobile Device} Berbasis \textit{Proxy}

### 2016-11-01 Paper/23215131-Aris Prawisudatama-Paper Thesis-3rd Rev/Paper.tex
Update testing result
Commit all

\begin{document}
%
% paper title
% Titles are generally capitalized except for words such as a, an, and, as,
% at, but, by, for, in, nor, of, on, or, the, to and up, which are usually
% not capitalized unless they are the first or last word of the title.
% Linebreaks \\ can be used within to get better formatting as desired.
% Do not put math or special symbols in the title.
\title{Design and Implementation of Mobile Proxy\\ Case Study: Mobile Data Collection}

@@

\begin{figure}
    \centering
    \includegraphics[width=8.5cm]{../Images/proxy-overview}
    \caption{Proxy Overview}
    \label{fig:proxy-overview}
\end{figure}

@@

\begin{figure}
    \centering
    \includegraphics[width=8cm]{../Images/ws-standards-stack}
    \caption{Web Service Standards Stack}
    \label{fig:ws-standards-stack}
\end{figure}

@@

\begin{figure}
    \centering
    \includegraphics[width=8cm]{../Images/proxy-design-data-layers}
    \caption{Data Bus Layers}
    \label{fig:proxy-design-data-layers}
\end{figure}

@@

\begin{figure}
	\centering
	\subfloat[Web Services Replication Strategy]{
		\centering
		\includegraphics[width=3.5cm]{../Images/bundle-replication-flowchart}
		\label{fig:bundle-replication-flowchart}
	}
	\hfil\hfil
	\subfloat[Data Replication Strategy]{
		\centering
		\includegraphics[width=3.5cm]{../Images/data-replication-flowchart}
		\label{fig:data-replication-flowchart}}
	\caption{Replication Strategies}
	\label{fig:replication-flowchart}
\end{figure}

@@

\begin{figure}
    \centering
    \includegraphics[width=8cm]{../Images/data-sync-flowchart}
    \caption{Data Syncronization Strategy}
    \label{fig:data-sync-flowchart}
\end{figure}

@@

\begin{figure}
    \centering
    \includegraphics[width=6cm]{../Images/routing-flowchart}
    \caption{Routing Strategy}
    \label{fig:routing-flowchart}
\end{figure}

@@

\begin{figure}
	\centering
	\subfloat[Home Page]{
		\centering
		\includegraphics[width=2.5cm]{../Images/android-app-1}
		\label{fig:android-app-1}
	}
	\hfil
	\subfloat[Autostart OSGi Framework]{
		\centering
		\includegraphics[width=2.5cm]{../Images/android-app-2}
		\label{fig:android-app-2}}
	\hfil
	\subfloat[Bundle Page]{
		\centering
		\includegraphics[width=2.5cm]{../Images/android-app-3}
		\label{fig:android-app-3}}
	\caption{Android Application}
	\label{fig:android-app}
\end{figure}

@@

\begin{figure}
	\centering
	\subfloat[Install bundle]{
		\centering
		\includegraphics[width=2.5cm]{../Images/android-bundle-1}
		\label{fig:android-bundle-1}}
	\hfil
	\subfloat[Bundle is installing]{
		\centering
		\includegraphics[width=2.5cm]{../Images/android-bundle-2}
		\label{fig:android-bundle-2}}
	\hfil
	\subfloat[Bundles are installed]{
		\centering
		\includegraphics[width=2.5cm]{../Images/android-bundle-3}
		\label{fig:android-bundle-3}}
	\vfil
	\subfloat[Bundle is starting]{
		\centering
		\includegraphics[width=2.5cm]{../Images/android-bundle-4}
		\label{fig:android-bundle-4}}
	\hfil
	\subfloat[Bundles are active]{
		\centering
		\includegraphics[width=2.5cm]{../Images/android-bundle-5}
		\label{fig:android-bundle-5}}
	\hfil
	\subfloat[Composite application is loaded]{
		\centering
		\includegraphics[width=2.5cm]{../Images/android-bundle-6}
		\label{fig:android-bundle-6}}
	\caption{Android Bundles}
	\label{fig:android-bundle}
\end{figure}

@@

\section{Testing}
\subsection{Response Time}
\begin{table}
% increase table row spacing, adjust to taste
\renewcommand{\arraystretch}{1.3}
% if using array.sty, it might be a good idea to tweak the value of
% \extrarowheight as needed to properly center the text within the cells
\caption{Response Time Test (ms)}
\label{tbl:response_time}
\centering
%% Some packages, such as MDW tools, offer better commands for making tables
%% than the plain LaTeX2e tabular which is used here.
\begin{tabular}{|c||c|c|c|c|c|c|}
\hline
Transactions & \multicolumn{3}{|c|}{Without Proxy} & \multicolumn{3}{|c|}{With Proxy}\\
\hline
& Total & $\mu$ & $\sigma$ & Total & $\mu$ & $\sigma$\\
\hline
5 & 5043 &  &  & 121 &  & \\
\hline
110 & 50439 &  &  & 7442 &  & \\
\hline
1100 & 668605 &  &  & 405408 &  & \\
\hline
5500 & 2658179 &  &  & 2415957 &  & \\
\hline
\end{tabular}
\end{table}

@@

\bibliographystyle{IEEEtran}
\bibliography{IEEEabrv,../Bibliography/Paper}

>>>>

\begin{document}
%
% paper title
% Titles are generally capitalized except for words such as a, an, and, as,
% at, but, by, for, in, nor, of, on, or, the, to and up, which are usually
% not capitalized unless they are the first or last word of the title.
% Linebreaks \\ can be used within to get better formatting as desired.
% Do not put math or special symbols in the title.
\title{Design and Implementation Mobile Data Collection\\Using Mobile Proxy}

@@

\begin{figure}
    \centering
    \includegraphics[width=8.5cm]{../../Resources/Images/proxy-overview}
    \caption{Proxy Overview}
    \label{fig:proxy-overview}
\end{figure}

@@

\begin{figure}
    \centering
    \includegraphics[width=8cm]{../../Resources/Images/ws-standards-stack}
    \caption{Web Service Standards Stack}
    \label{fig:ws-standards-stack}
\end{figure}

@@

\begin{figure}
    \centering
    \includegraphics[width=8cm]{../../Resources/Images/proxy-design-data-layers}
    \caption{Data Bus Layers}
    \label{fig:proxy-design-data-layers}
\end{figure}

@@

\begin{figure}
	\centering
	\subfloat[Web Services Replication Strategy]{
		\centering
		\includegraphics[width=3.5cm]{../../Resources/Images/bundle-replication-flowchart}
		\label{fig:bundle-replication-flowchart}
	}
	\hfil\hfil
	\subfloat[Data Replication Strategy]{
		\centering
		\includegraphics[width=3.5cm]{../../Resources/Images/data-replication-flowchart}
		\label{fig:data-replication-flowchart}}
	\caption{Replication Strategies}
	\label{fig:replication-flowchart}
\end{figure}

@@

\begin{figure}
    \centering
    \includegraphics[width=8cm]{../../Resources/Images/data-sync-flowchart}
    \caption{Data Syncronization Strategy}
    \label{fig:data-sync-flowchart}
\end{figure}

@@

\begin{figure}
    \centering
    \includegraphics[width=6cm]{../../Resources/Images/routing-flowchart}
    \caption{Routing Strategy}
    \label{fig:routing-flowchart}
\end{figure}

@@

\begin{figure}
	\centering
	\subfloat[Home Page]{
		\centering
		\includegraphics[width=2.5cm]{../../Resources/Images/android-app-1}
		\label{fig:android-app-1}
	}
	\hfil
	\subfloat[Autostart OSGi Framework]{
		\centering
		\includegraphics[width=2.5cm]{../../Resources/Images/android-app-2}
		\label{fig:android-app-2}}
	\hfil
	\subfloat[Bundle Page]{
		\centering
		\includegraphics[width=2.5cm]{../../Resources/Images/android-app-3}
		\label{fig:android-app-3}}
	\caption{Android Application}
	\label{fig:android-app}
\end{figure}

@@

\begin{figure}
	\centering
	\subfloat[Install bundle]{
		\centering
		\includegraphics[width=2.5cm]{../../Resources/Images/android-bundle-1}
		\label{fig:android-bundle-1}}
	\hfil
	\subfloat[Bundle is installing]{
		\centering
		\includegraphics[width=2.5cm]{../../Resources/Images/android-bundle-2}
		\label{fig:android-bundle-2}}
	\hfil
	\subfloat[Bundles are installed]{
		\centering
		\includegraphics[width=2.5cm]{../../Resources/Images/android-bundle-3}
		\label{fig:android-bundle-3}}
	\vfil
	\subfloat[Bundle is starting]{
		\centering
		\includegraphics[width=2.5cm]{../../Resources/Images/android-bundle-4}
		\label{fig:android-bundle-4}}
	\hfil
	\subfloat[Bundles are active]{
		\centering
		\includegraphics[width=2.5cm]{../../Resources/Images/android-bundle-5}
		\label{fig:android-bundle-5}}
	\hfil
	\subfloat[Composite application is loaded]{
		\centering
		\includegraphics[width=2.5cm]{../../Resources/Images/android-bundle-6}
		\label{fig:android-bundle-6}}
	\caption{Android Bundles}
	\label{fig:android-bundle}
\end{figure}

@@

\section{Testing}
\subsection{Response Time}
Pengujian terhadap response time digunakan untuk mengukur latency antara client dan server. Pengujian ini menggunakan dua skenario, yaitu skenario tanpa proxy dan dengan proxy. Dari empat kali pengujian dengan jumlah transaksi yang bervariasi, seperti yang ditunjukkan dalam Table \ref{tbl:response_time}, menunjukkan dengan menggunakan proxy dapat mengurangi response time sebanyak 20 kali lipat dibandingkan dengan tanpa menggunakan proxy.

\begin{table}
\renewcommand{\arraystretch}{1.3}
\caption{Response Time Test (ms)}
\label{tbl:response_time}
\centering
\begin{tabular}{|c||c|c|c|c|c|c|}
\hline
Transactions & \multicolumn{3}{c|}{Without Proxy} & \multicolumn{3}{c|}{With Proxy}\\
\hline
& Total & $\mu$ & $\sigma$ & Total & $\mu$ & $\sigma$\\
\hline
11 & 4226 & 384.18 & 77.10 & 862 & 78.36 & 224.09\\
\hline
110 & 41999 & 381.81 & 51.54 & 1376 & 12.51 & 9.41\\
\hline
1100 & 405892 & 368.99 & 59.95 & 15891 & 14.45 & 13.47\\
\hline
5500 & 2226949 & 404.90 & 206.73 & 64600 & 11.74 & 9.92\\
\hline
\end{tabular}
\end{table}

@@

\bibliographystyle{IEEEtran}
\bibliography{IEEEabrv,../../Resources/Bibliography/Paper.bib}

### 2016-11-01 Thesis/8th Revision/main.tex
Commit all

\documentclass[12pt,a4paper,oneside]{book}
\input{title}
\usepackage{tabularx}
\usepackage{times}
\usepackage{array}
\usepackage{tcolorbox}
\usepackage{pbox}
\usepackage{multirow}
\usepackage{amssymb}
\usepackage{framed}
\usepackage{amsmath}
\usepackage{multirow}
\usepackage{tabu}
\usepackage[T1]{fontenc}
\usepackage{booktabs}
\usepackage{afterpage}
\usepackage{caption}
\usepackage{subcaption}
\newcommand{\squeezeup}{\vspace{-7mm}}
\numberwithin{equation}{chapter} 
\usepackage{cite}
\usepackage{float}
\floatstyle{plaintop}
\restylefloat{table}

\title{Desain dan Implementasi \textit{Mobile Proxy} \\Studi Kasus Pengumpulan Data Lapangan Berbasis Mobile}
\author{Aris Prawisudatama\\23215131}
\englishtitle[Design and Implementation of Mobile Proxy \\Case Study Mobile Data Collection]
\englishprodi[Magister Teknik Elektro]

@@

\frontmatter
\makecustomtitle{images/gajah.png}
\pembimbingsatu{{\footnotesize Dr. I Gusti Bagus Baskara Nugraha}}{197601242010121001}
%\pembimbingdua{Dr. Pembimbing, S.T., M.T.}{999988771111223333}
\makecustompengesahan

\begin{abstrak}[indo]
Lorem ipsum dolor sit amet, ex nostrud nostrum his. Sea cu fierent splendide. Alienum gloriatur vim at, pro ei sumo epicurei. Eos ne quidam expetendis, illum debet dissentiunt eu vel, no mei denique lobortis.

Kata Kunci: \textit{Lorem, Ipsum, Dolor}

\end{abstrak}
\begin{abstrak}[english]
Fugit adversarium ex mea, ne doctus volumus usu. Eu essent dissentiunt vel. Pri no munere consulatu neglegentur, his no erant recteque. Eu odio laoreet per, te eum consul bonorum impedit, quas utinam nostrud vel an. Pri prima noluisse tractatos et, case dicant gubergren ei cum.

Keywords: \textit{Lorem, Ipsum, Dolor}
\end{abstrak}

@@

\begin{center}
\textbf{\textit{"The only thing we're allowed to is to believe that we won't regret the choice we made."}}. \\
\textbf{\textit{"The world is merciless, and it's also very beautiful."}} \\
(Hajime Isayama)
\end{center}

@@

\begin{flushright}
Bandung, Februari 2015\\[2cm]
Nama Mahasiswa
\end{flushright} 
\end{custompage}

@@

\mainmatter
\input{bab1}
\input{bab2}
\input{bab3}

\backmatter
\bibliographystyle{ieeetr}
\addcontentsline{toc}{chapter}{\bibname}
\bibliography{thesis}
\appendix
\input{appendix1}

>>>>

\documentclass[12pt,a4paper,oneside]{book}
\input{title}
\usepackage{tabularx}
\usepackage{times}
\usepackage{array}
\usepackage{tcolorbox}
\usepackage{pbox}
\usepackage{multirow}
\usepackage{amssymb}
\usepackage{framed}
\usepackage{amsmath}
\usepackage{multirow}
\usepackage{tabu}
\usepackage[T1]{fontenc}
\usepackage{booktabs}
\usepackage{afterpage}
\usepackage{caption}
\usepackage{subcaption}
\usepackage{hyperref}
\newcommand{\squeezeup}{\vspace{-7mm}}
\numberwithin{equation}{chapter} 
\usepackage{cite}
\usepackage{float}
\floatstyle{plaintop}
\restylefloat{table}

\urlstyle{same}

%\title{Desain dan Implementasi \textit{Mobile Proxy} \\Studi Kasus Pengumpulan Data Lapangan Berbasis Mobile}
\title{Desain dan Implementasi Pengumpulan Data Menggunakan \textit{Mobile Device} Berbasis \textit{Proxy}}
\author{Aris Prawisudatama\\23215131}
%\englishtitle[Design and Implementation of Mobile Proxy \\Case Study Mobile Data Collection]
\englishtitle[Design and Implementation Proxy-based Mobile Data Collection]
\englishprodi[Magister Teknik Elektro]

@@

\frontmatter
\makecustomtitle{../../Resources/Images/gajah.png}
\pembimbingsatu{{\footnotesize Dr. I Gusti Bagus Baskara Nugraha}}{197601242010121001}
%\pembimbingdua{Dr. Pembimbing, S.T., M.T.}{999988771111223333}
\makecustompengesahan

\begin{abstrak}[indo]
Abstrak bahasa Indonesia

Kata Kunci: \textit{Pengumpulan, Data, Mobile, Device, Proxy}

\end{abstrak}
\begin{abstrak}[english]
English abstract

Keywords: \textit{Data, Collection, Mobile, Device, Proxy}
\end{abstrak}

@@

\begin{center}
\textbf{Engkau tak dapat meraih ilmu kecuali dengan enam hal yaitu cerdas, selalu ingin tahu, tabah, punya bekal dalam menuntut ilmu, bimbingan dari guru dan dalam waktu yang lama}.
(Ali bin Abi Thalib)
\end{center}

@@

\begin{flushright}
Bandung, Februari 2016\\[2cm]
Aris Prawisudatama
\end{flushright} 
\end{custompage}

@@

\mainmatter
\input{bab1}
\input{bab2}
\input{bab3}
\input{bab4}

\backmatter
\bibliographystyle{ieeetr}
\addcontentsline{toc}{chapter}{\bibname}
\bibliography{../../Resources/Bibliography/Paper}
\appendix
\input{appendix1}
